Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-07-16 Cost_manuscript.Rmd
modified trialwise model

```{r Setups, include = FALSE}
## libraries
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
#library(lmerTest)
library(gridExtra)
library(reshape2)
library(corrplot)
library(survival)
library(ggfortify)
library(patchwork)

@@

  return(adapted_p)
}
```

>>>>

```{r Setups, include = FALSE, warning = FALSE}
## libraries
library(tidyverse)
library(ggfortify)
library(knitr)
library(pander) 
library(nloptr)
library(pwr)
library(lme4)
#library(lmerTest)
library(gridExtra)
library(reshape2)
library(corrplot)
library(survival)
library(ggfortify)
library(patchwork)

@@

  return(adapted_p)
}

# remove break time and start counting from 0
standardize_time <- function(subjData) {
  # remove the break time (variable across subjects) and start counting time from 0 (otherwise it can add physical effort calibration)
  breakTime <- min(subjData$ExpTime[subjData$Block == 4]) - max(subjData$ExpTime[subjData$Block == 3])
  subjData$ExpTime[which(subjData$Block > 3)] <- subjData$ExpTime[which(subjData$Block > 3)] - breakTime + 16
  subjData$ExpTime <- subjData$ExpTime - min(subjData$ExpTime)

  return(subjData)
}
```
